---
title: "GESIS Political Science Roundtable (PSRT)"
subtitle: "Conference Program"
date: "June 15, 2026"
date-format: long
format:
  pdf:
    documentclass: article
    papersize: a4
    geometry:
      - margin=2.5cm
    include-in-header: _preamble.tex
    toc: false
    number-sections: false
    keep-tex: true
params:
  venue: "GESIS -- Leibniz Institute for the Social Sciences, Cologne"
  schedule_csv: "data/schedule.csv"
  papers_csv: "data/papers.csv"
  panel_prefix: "Panel: "
  schedule_only: false
  panel_clearpage: true
  panel_show_time: true
  type_icons:
    value:
      paper: "P"
      presentation: "T"
      lightning: "L"
---

```{r}
#| echo: false
#| label: setup

# -- Read params and data --------------------------------------------------
VENUE <- params$venue
PANEL_PREFIX <- params$panel_prefix
TYPE_ICONS <- params$type_icons
SCHEDULE_ONLY <- params$schedule_only

schedule <- read.csv(params$schedule_csv, stringsAsFactors = FALSE, strip.white = TRUE)
papers <- read.csv(params$papers_csv, stringsAsFactors = FALSE, strip.white = TRUE)

# -- Helpers ---------------------------------------------------------------
tex_escape <- function(text) {
  text <- gsub("\\\\", "\\\\textbackslash{}", text)
  text <- gsub("&", "\\\\&", text)
  text <- gsub("%", "\\\\%", text)
  text <- gsub("\\$", "\\\\$", text)
  text <- gsub("#", "\\\\#", text)
  text <- gsub("_", "\\\\_", text)
  text <- gsub("\\{", "\\\\{", text)
  text <- gsub("\\}", "\\\\}", text)
  text <- gsub("~", "\\\\textasciitilde{}", text)
  text <- gsub("\\^", "\\\\textasciicircum{}", text)
  text
}

make_slug <- function(text) {
  slug <- tolower(trimws(text))
  slug <- gsub("[^a-z0-9]+", "-", slug)
  slug <- gsub("^-|-$", "", slug)
  slug
}

get_panel_display_name <- function(title) {
  if (startsWith(title, PANEL_PREFIX)) {
    return(substring(title, nchar(PANEL_PREFIX) + 1))
  }
  title
}

get_type_icon <- function(ptype) {
  ptype <- tolower(trimws(ptype))
  letter <- if (ptype %in% names(TYPE_ICONS)) TYPE_ICONS[[ptype]] else ptype
  paste0("\\typeicon{", tex_escape(letter), "}")
}

has_dates <- "date" %in% names(schedule)
multi_day <- has_dates && length(unique(schedule$date)) > 1

# -- Build panel lookup: panel_id -> display name --------------------------
panel_schedule <- schedule[tolower(schedule$type) == "panel", ]
panel_display_names <- setNames(
  sapply(panel_schedule$title, get_panel_display_name),
  panel_schedule$panel_id
)
```

```{r}
#| echo: false
#| output: asis
if (SCHEDULE_ONLY) {
  cat("````{=latex}\n")
  cat("\\pagestyle{empty}\n")
  cat("````\n")
}
```

\begin{center}
{\small `r tex_escape(VENUE)`}
\end{center}

## Schedule

```{r}
#| echo: false
#| output: asis

# -- Build schedule table --------------------------------------------------
rows <- list()

for (i in seq_len(nrow(schedule))) {
  time_str <- schedule$time[i]
  title <- schedule$title[i]
  item_type <- tolower(schedule$type[i])

  # Multi-day: insert date header row
  if (multi_day) {
    row_date <- schedule$date[i]
    if (i == 1 || row_date != schedule$date[i - 1]) {
      rows[[length(rows) + 1]] <- data.frame(
        Time = paste0("\\textbf{\\sffamily ", tex_escape(row_date), "}"),
        Content = ""
      )
    }
  }

  if (item_type == "break") {
    rows[[length(rows) + 1]] <- data.frame(
      Time = paste0("\\textcolor{gray}{\\textsf{", tex_escape(time_str), "}}"),
      Content = paste0("\\textit{", tex_escape(title), "}")
    )

  } else if (item_type == "event") {
    rows[[length(rows) + 1]] <- data.frame(
      Time = paste0("\\textsf{", tex_escape(time_str), "}"),
      Content = tex_escape(title)
    )

  } else if (item_type == "panel") {
    pid <- schedule$panel_id[i]
    panel_name <- panel_display_names[[pid]]
    slug <- make_slug(pid)
    if (SCHEDULE_ONLY) {
      panel_content <- paste0("\\textbf{", tex_escape(panel_name), "}")
    } else {
      panel_content <- paste0("\\textbf{\\hyperlink{", slug, "}{", tex_escape(panel_name), "}}")
    }
    rows[[length(rows) + 1]] <- data.frame(
      Time = paste0("\\textsf{", tex_escape(time_str), "}"),
      Content = panel_content
    )

    # Add paper rows under this panel
    panel_papers <- papers[papers$panel_id == pid, ]
    for (j in seq_len(nrow(panel_papers))) {
      pp <- panel_papers[j, ]
      paper_slug <- make_slug(paste(pp$author, pp$title))
      icon <- get_type_icon(pp$type)
      if (SCHEDULE_ONLY) {
        paper_title <- tex_escape(pp$title)
      } else {
        paper_title <- paste0("\\hyperlink{", paper_slug, "}{", tex_escape(pp$title), "}")
      }
      rows[[length(rows) + 1]] <- data.frame(
        Time = "",
        Content = paste0(
          "\\hspace{1.2em}", icon, "\\hspace{0.3em}",
          "{\\small ", tex_escape(pp$author), " -- ", paper_title, "}"
        )
      )
    }
  }
}

schedule_df <- do.call(rbind, rows)

# Render as LaTeX table
tbl <- knitr::kable(
  schedule_df,
  format = "latex",
  booktabs = TRUE,
  escape = FALSE,
  col.names = NULL,
  linesep = ""
)

# Full width, remove top/bottom rules, increase row padding
tbl <- gsub("\\\\begin\\{tabular\\}\\{ll\\}", "\\\\renewcommand{\\\\arraystretch}{1.4}\n\\\\begin{tabularx}{\\\\textwidth}{lX}", tbl)
tbl <- gsub("\\\\end\\{tabular\\}", "\\\\end{tabularx}", tbl)
tbl <- gsub("\\\\toprule", "", tbl)
tbl <- gsub("\\\\bottomrule", "", tbl)

cat(tbl)
```

\vspace{1em}

## Additional information

In case you have any questions about the schedule or the papers, please contact the organizers.



```{r}
#| echo: false
#| output: asis

# -- Legend -----------------------------------------------------------------
cat("````{=latex}\n")
cat("\\vfill\n")
cat("\\hrule\n")
cat("\\vspace{0.3em}\n")
cat("{\\small ")
cat(paste(
  sapply(names(TYPE_ICONS), function(t) {
    paste0("\\typeicon{", tex_escape(TYPE_ICONS[[t]]), "}\\,=\\,", tex_escape(t))
  }),
  collapse = " \\qquad "
))
cat("}\n")
cat("````\n")
```


```{r}
#| echo: false
#| output: asis
if (!SCHEDULE_ONLY) cat("\n\\newpage\n")
```

```{r}
#| echo: false
#| output: asis
#| eval: !expr '!params$schedule_only'

# -- Abstracts -------------------------------------------------------------
cat("````{=latex}\n")

# Get panel IDs in schedule order
seen_pids <- unique(panel_schedule$panel_id)

# Build a lookup: panel_id -> start--end time
panel_time_ranges <- sapply(seq_len(nrow(panel_schedule)), function(k) {
  row_idx <- which(schedule$panel_id == panel_schedule$panel_id[k] &
                   schedule$time == panel_schedule$time[k])[1]
  start <- panel_schedule$time[k]
  end <- if (row_idx < nrow(schedule)) schedule$time[row_idx + 1] else ""
  time_str <- if (end != "") paste0(start, "--", end) else start
  if (multi_day) {
    panel_date <- schedule$date[row_idx]
    time_str <- paste0(panel_date, ", ", time_str)
  }
  time_str
})
names(panel_time_ranges) <- panel_schedule$panel_id

for (idx in seq_along(seen_pids)) {
  pid <- seen_pids[idx]
  panel_name <- panel_display_names[[pid]]
  slug <- make_slug(pid)

  # Clearpage before each panel (except the first)
  if (params$panel_clearpage && idx > 1) {
    cat("\\clearpage\n")
  }

  cat("\\hypertarget{", slug, "}{}\n", sep = "")
  if (params$panel_show_time && pid %in% names(panel_time_ranges)) {
    cat("\\panelsection[", tex_escape(panel_time_ranges[[pid]]), "]{", tex_escape(panel_name), "}\n\n", sep = "")
  } else {
    cat("\\panelsection{", tex_escape(panel_name), "}\n\n", sep = "")
  }

  panel_papers <- papers[papers$panel_id == pid, ]
  for (j in seq_len(nrow(panel_papers))) {
    pp <- panel_papers[j, ]
    paper_slug <- make_slug(paste(pp$author, pp$title))
    ptype <- tolower(trimws(pp$type))
    icon <- get_type_icon(ptype)

    cat("\\needspace{5\\baselineskip}\n")
    cat("\\hypertarget{", paper_slug, "}{}\n", sep = "")
    cat("\\paperentry{", tex_escape(pp$title), "}{", tex_escape(pp$author), "}{", icon, "}{", tex_escape(ptype), "}\n\n", sep = "")
    cat(tex_escape(trimws(pp$abstract)), "\n\n")

    if (j < nrow(panel_papers)) {
      cat("\\paperseparator\n\n")
    }
  }
}

cat("````\n")
```
